My title

### 2024-03-14 paper/paper.qmd
Update data

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hailey Jang
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hailey Jang
thanks: "Code and data are available at: https://github.com/Hailey-Jang/Suicide-and-Homelessness.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
